### 2015-07-07 text/ms.Rmd
Major re-work of text; bring in 'superensembles'

@@

<!--200 words-->

What can we do when multiple ecological models suggest different conclusions about population status? Any single model is unlikely to perform best under all scenarios. Ensemble methods, commonly used in fields such as climate science, provide a powerful tool to leverage information across multiple ecological models. Here we evaluate the potential for ensemble methods to improve estimates of fish population status and trajectory. We fit four data-limited models of population and exploitation dynamics and combine their estimates of the mean and slope of biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with four ensemble models: a simple average, a linear model, and two machine-learning methods---random forests and boosted regression trees. We build our ensembles on a simulated dataset of 5760 fish stocks and test our models with cross-validation and a global database of `r ram_stocks_n` stock assessments. We find that ensemble models substantially improve estimates of population status and trajectory. Machine-learning ensembles performed the best: accuracy improved `r mean_sim$mach_vs_ind_mare_fold`%, correlation improved from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median proportional error) declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We found similar improvements when predicting the slope of status. When the simulation-trained ensembles were applied to global fish stocks, the best ensembles still improved all dimensions of performance over the next-best individual model. Ensemble models have potential to improve estimates of population status and trajectory across many taxa beyond fish. 
However, ensemble methods must be carefully tested, formed from a diverse set of accurate models, and built on a dataset sufficiently representative of the populations they are applied to.

<!-- 3-6 keywords -->
Keywords: data-limited fisheries, model averaging, population dynamics, ... *(up to 6)*

@@

There are often multiple models we can apply to an ecological system
[@hilborn1997; @burnham2002]. Models might incorporate different data types,
assume alternate population dynamics, or make contrasting assumptions about the
starting state of a system. These models may suggest different conclusions
about population status and trajectory and we often do not know which model is
best. How can we reconcile multiple models to make robust management decisions
about ecological resources?

Ensemble methods, which combine the output from multiple models as predictors
in a new 'ensemble' model, are one possible solution to this problem. A simple
ensemble model might take the average of multiple model predictions, perhaps
weighted by some goodness of fit. A complex ensemble model might also take into
account non-linear interactions between model predictions and additional
covariates. Ensemble models are popular in other fields including public health
[@thomson2006], agriculture [@cantelaube2005], climate science [@murphy2004;
@tebaldi2007; @pierce2009], and machine learning [@dietterich2000]. 
<!--We think they have tremendous opportunity in ecological resource management.-->

In fisheries science, a common task is estimating the status and trajectory of
an exploited fish population. For the majority of fish stocks, we have limited
fisheries independent data to estimate stock status [@fao2014]. In recent
years, a number of methods have been proposed to derive population status based
on the limited information that is broadly available: fisheries catch time
series and basic knowledge about the productivity of the species (e.g.
[@vasconcellos2005; @martell2013]). Recently, Rosenberg et al. [@rosenberg2014]
investigated the ability for four such models to estimate population status through
a large-scale simulation experiment. A key finding was that these models
frequently disagree on population status and any one model has relatively poor
predictive ability on average (e.g. Fig. \ref{motivate}).

<!--
Exploit interactions between individual models and relationships between other conditions of the data and the performance of the individual models. Fitted to populations of known or assumed status and this ensemble model is used to extrapolate to populations of interest.
-->

Here, we develop ensemble models to estimate the population status and
trajectory of exploited fish populations. We explore a variety of ensemble
approaches applied to both simulated and real-world fish stocks and compare
predictive performance. In developing these models we highlight the types of
challenges one encounters when forming and evaluating ensemble models. We find
that ensembles generally provide improved predictive performance over any
single model---especially when considered across multiple dimensions of
predictive ability and across multiple datasets. Furthermore, the output from
ensemble models can provide better mechanistic understanding of how individual
models of status and trajectory perform.

@@

We first developed and tested ensemble models with a fully factorial simulated
dataset [@rosenberg2014]. These previously published simulation models included
three life histories: small pelagic, demersal, large pelagic; three levels of
how depleted biomass was at the start of the dataset compared to carrying
capacity: 100%, 70%, and 40% of carrying capacity; and four exploitation
dynamics: a constant exploitation rate, a exploitation rate that is coupled
with biomass to mimic an open-access single-species fishery, a scenario where
exploitation rate increases to a fixed level, and a 'roller-coaster' scenario
where the exploitation rate increases and then decreases. Process noise was
introduced to the models through two levels of multiplicative recruitment
variability: $N(0, 0.2)$ and $N(0, 0.6)$, and that process noise was either
uncorrelated or had a first-order autoregressive correlation of 0.6. The
simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

Rosenberg et al. [@rosenberg2014] ran ten iterations for each combination of
factors adding stochastic draws of recruitment and catch-recording variability
each time to generate a total of 5760 stocks. The simulation models were built
in the package `FLR` [@kell2007] for the statistical software \textsf{R}
[@r2015]. The code to generate the simulations is available at
<https://github.com/flr/StockSims> (TODO: not there).

We also tested our ensemble models on the RAM Legacy Stock Assessment Database
[@ricard2012]. Our analysis of the stock-assessment database was based on
version XX downloaded on XX. After removing stocks for which the models
described below did not converge, this database included `r ram_stocks_n`
stocks.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year,
$B_t$ represents biomass at time $t$, $r$ represents the intrinsic population
growth rate, $B_0$ represents unfished biomass or carrying capacity, and $C$
represents catch. Rosenberg et al. [@rosenberg2014] provide a full summary of
these four methods and code to fit all the models is available in an
accompanying package `datalimited` for the statistical software \textsf{R}. In
summary:

* *COM-SIR* (catch-only-model with sample-importance-resampling) is a coupled
  harvest-dynamics model @vasconcellos2005. Biomass is assumed to follow a
  Schaefer model and harvest dynamics are assumed to follow a logistic model.
  The model is fit with a sample-importance-sampling algorithm [@rosenberg2014].

@@

* *SSCOM* (state-space catch-only model) TODO: Jim -- can you give a ~2 sentence summary?

* *mPRM* (modified panel regression model) is a modified version of the
  panel-regression model from Costello et al. [@costello2012]. Unlike the other
  models, mPRM is empirical and not mechanistic---it uses the RAM
  Legacy Stock Assessment database to fit a regression model to a series of
  characteristics of the catch time series and stock with stock-assessed
  $B/B_\mathrm{MSY}$ as the response. The model used in this paper is
  modified from the original in that it condenses the life-history categories
  into three categories to match the simulated dataset, removes the maximum
  catch predictor since the absolute catch in the simulated dataset is
  arbitrary, and does not implement the bias correction needed in Costello et
  al. [@costello2012] for deriving aggregate estimates of mean status across
  multiple stocks.

@@

Ensemble methods allow us to incorporate additional covariates 
and potentially leverage interactions between these covariates and individual
model predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. For simplicity, and to allow us to apply models
developed with the simulated dataset to the real-world dataset, we added only one
set of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the statistical properties of the catch series
that is independent of time series length and absolute magnitude of catch. We fit
spectral models to the scaled catch time series (catch divided by maximum
catch) with the `spec.ar` function in \textsf{R} and recorded representative
short- and long-term spectral densities at frequencies of 0.20 and 0.05, which
correspond to 5- and 20-year cycles.

## Ensemble models

The individual models we seek to combine with ensemble models provide time
series of $B/B_\mathrm{MSY}$. Therefore, we can use ensemble models to estimate multiple
properties of these status time series. Here, we focus on two properties: the
mean and slope of $B/B_\mathrm{MSY}$ in the last 5 years. Together, these quantities
address the recent state and trajectory of status, which are both of management
and conservation interest (e.g. [@mace2008]). To avoid undue influence of the
end points of the time series on the calculated slope, we measured the slope as
the Theil-Sen estimator of median slope [@theil1950].

Here we compare four ensemble models of varying complexity: an average, a
linear model with two-way interactions, a random forest, and boosted regression
tree. The general form of our models was

@@

\noindent 
where $L$ is a generalized loss function, $f$ is some generalized regression
function, $\hat{b}_\mathrm{CMSY}$ is the mean or slope prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $S(0.2)$ and $S(0.05)$ represent the
spectral density of the scaled catch series at frequencies of 0.20 and 0.05, $b$
is the mean or slope value the model is fitted to, and $\theta$ is the set of
parameters for the regression function. For all ensemble models of mean
$B/B_\mathrm{MSY}$---a ratio bounded at zero---we fit the models in log space and
exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, we fit
ensemble models on the natural untransformed scale.

We calculated the average ensemble models as the geometric mean of the
individual model $B/B_\mathrm{MSY}$ estimates and the mean of the individual model
$B/B_\mathrm{MSY}$ slopes. We fit the linear model ensemble with second-order
interactions. We fit two machine learning ensemble models based on regression
trees. Regression trees sequentially determine what value of a predictor best
splits the response data into two 'branches' based on a specified loss
function [@breiman1984]. In random forests, a series of regression trees are
built on a random subset of the data and random subset of the covariates of the
model [@breiman2001]. In generalized boosted models (GBMs), each subsequent
model is fit to the residuals from the previous model; data points that are fit
poorly in a given model are given more weight in the next model [@elith2008].
Random forests and GBMs can provide strong predictive performance and fit
highly non-linear relationships [@elith2008; @hastie2009]. We fit random forest
models with the `randomForest` package [@liaw2002] for \textsf{R} with the
default argument values. We fit boosted regression tree models with the `gbm`
package [@ridgeway2015] for \textsf{R}. Based on cross-validation with the
**caret** \textsf{R} package, we fit GBMs with 2000 trees, an interaction depth
of $6$, a learning rate (shrinkage parameter) of $0.01$, and all other
arguments at their default values.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations (e.g. [@walther2005]). Here,
we measure proportional error, defined as
$(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true'
(or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional
error to measure bias, median absolute proportional error to measure accuracy,
and Spearman's rank-order correlation to measure the ability to correctly rank
populations.

@@

Ensemble models, and in particular the machine learning ensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning ensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These ensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning ensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting slope (SSCOM; Fig.
\ref{performance-sim-slope}).

The ensemble models were able to improve the predictions of status by
exploiting the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high prediction
clusters (Fig. \ref{partial-sim}). Ensembles also exploited the covariance
between individual model predictions. For instance, both the linear model and
GBM ensemble suggest that if mPRM and SSCOM predict high status, the true
status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The
addition of spectral density covariates helped the ensemble models correctly
predict higher status values (Fig. \ref{hexagon}g, h) by exploiting
interactions between the spectral density predictors and the individual model
predictions (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally
degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

@@

Ensemble methods provide a useful approach to situations where conservation and
management decisions must be made on the basis of multiple, potentially
contrasting estimates of status---a situation common to many ecological
settings beyond fisheries. Compared to individual models of fish population
status, ensemble models were consistently the best or among the best across
three performance dimensions (accuracy, bias, and rank-order performance), two
response variables (status and trajectory), two datasets (simulated and global
fisheries), and multiple ensemble model types (from a simple average to machine
learning models). Our results suggest choosing an ensemble model that allows
for non-parametric relationships, such as machine learning methods---these
methods provide added insight into individual model behaviour and generally
performed the best---but even a simple average of predictions across multiple
models may be useful.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make errors in
uncorrelated ways [@ali1996; @dietterich2000; @tebaldi2007]. Such
individual models would be expected to perform well in different conditions and
an ensemble model can exploit the best predictive performance of each. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to over-fitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we applied our ensembles to an
entirely new dataset (Fig. \ref{performance}b) and averages are a common
ensemble approach in climate science [@ipcc2013]. Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide a optimistically biased
impression of predictive performance if the training dataset fundamentally
differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble models
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on a averaging
*coefficients* whereas ensembles instead average *predictions*. By focussing on
predictions, ensembles do not suffer from the muddled inference of coefficient
averaging when coefficients covary [@cade2015] and are a more general purpose
tool: they do not require information theoretics, they can combine different
types of models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of ensemble models is that they can be tailored or specific response
variables. For example, we built separate ensemble models of mean $B/B_\mathrm{MSY}$ and
the slope of $B/B_\mathrm{MSY}$. The same set of model weights or non-linear
relationships need not hold across different response variables. For example,
SSCOM contributed little to the GBM ensemble estimate of status at higher
levels of predicted $B/B_\mathrm{MSY}$, but contributed strongly to estimates of slope
(TODO FIG). Formally, fitting ensemble models to specific quantities of
interest provides an additional calibration step [@rykiel1996]. Individual
models are typically calibrated (i.e. parameters are estimated) based on a
single response variable; however, this model might then provide a biased or
inaccurate estimate of other quantities of interest. For example, a
data-limited fisheries model might calibrate parameters by maximizing
likelihood with respect to observed and predicted catches but those parameters
may then provide a biased or inaccurate estimate of the mean and slope of
$B/B_\mathrm{MSY}$. Ensemble methods provide a final calibration step to a quantity of
interest. This ensemble calibration could further include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
low status levels than higher values.

>>>>

\noindent
Running head: Superensembles of population status

\begin{Large}
\noindent
Improving estimates of population status and trajectory with superensemble models
\end{Large}

@@

<!--up to 350 words-->

Ecological resource managers are often faced with reconciling multiple potentially
conflicting estimates of population status and trajectory.  One solution is to
average these predictions in an ensemble, but this approach ignores covariance
between models and may not optimally reduce bias and improve accuracy.
Superensemble models, commonly used in the fields of climate and weather
science, may provide a superior solution. Superensembles use the predictions
from multiple models as covariates in a new statistical model. Here we evaluate
the potential for ensemble and superensemble methods to improve estimates of fish population
status and trajectory. We fit four models of population and exploitation
dynamics to data-limited populations and combine their estimates of the mean and
slope of biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with an
ensemble average and three superensembles: a linear model, a random forest, and
a boosted regression tree. We build our models on a simulated dataset of 5760
fish stocks and test them with cross-validation and a global database of 
`r ram_stocks_n` stock assessments. 
We find that ensemble and superensemble models
substantially improve estimates of population status and trajectory.
Machine-learning superensembles performed the best for population status: accuracy improved
`r mean_sim$mach_vs_ind_mare_fold`%, correlation between predicted and true
status improved from 
`r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median
proportional error) declined from 
`r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. 
We found similar improvements when predicting the trajectory of status. When the
simulation-trained ensembles were applied to global fish stocks, the best
ensembles still improved all dimensions of performance over the next-best
individual model. Ensemble and superensemble models have the potential to
improve estimates of population status and trajectory across many taxa beyond
fish. However, they must be carefully tested, formed from a diverse set of
accurate models, and built on a dataset sufficiently representative of the
populations they are applied to.

<!-- up to 12 keywords -->
\noindent 
Keywords: data-limited fisheries, ensemble methods, model averaging, population dynamics, sustainable resource management

@@

Despite considerable advancements in the systematic collection of ecological
population data, we still have little data with which to estimate population
status for most species (IUCN, FAO, amphibian citations etc.). Yet, a large
portion of these data-limited populations face human-caused pressures and may
warrant conservation action (IUCN REF). This scenario calls for methods to
assess the status of populations that rely on limited sources of data. While,
such methods are increasingly available (e.g. REF, REF), their application faces
two key challenges: (1) performance is relatively poor compared to more
data-rich forms of population modelling (e.g. REF) and (2) resource managers are
often faced with reconciling multiple potentially conflicting estimates of
population status (e.g. REF).

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased
than individual model estimates and can integrate uncertainty in model
structure, initial conditions, and parameter estimation [@araujo2007]. For
instance, REF-international did this and REF-national did this.

Whereas averages or weighted averages can improve predictions, they may not
optimally leverage available data. Some models perform better than others in
certain conditions and the covariance between model predictions may contain
information that can both improve predictions and aid understanding of
individual model performance. We can exploit these characteristics by using the
predictions from a group of models as inputs into a separate statistical model.
This technique, sometimes called 'superensemble' modelling, is common in climate
and weather forecasting. The superensemble is fit to some training dataset where
outcomes are well known and used to predict on a separate dataset. For example,
@krishnamurti1999 combined predictions of wind and precipitation in Asian
monsoons via a superensemble regression fit to observed data. Their
superensemble considerably outperformed any individual prediction or weighted
average of predictions in terms of accuracy.

<!-- Ensemble methods, which combine the output from multiple models as
predictors in a new 'ensemble' model, are one possible solution to this
problem. A simple ensemble model might take the average of multiple model
predictions, perhaps weighted by some goodness of fit. A complex ensemble model
might also take into account non-linear interactions between model predictions
and additional covariates. Ensemble models are popular in other fields
including public health [@thomson2006], agriculture [@cantelaube2005], climate
science [@murphy2004; @tebaldi2007; @pierce2009], and machine learning
[@dietterich2000].-->

In fisheries science, a common task is estimating the status and trajectory of
an exploited fish population. For the majority of fish stocks, we have limited
fisheries independent data to estimate stock status [@fao2014]. In recent
years, a number of methods have been proposed to derive population status based
on the limited information that is broadly available: fisheries catch time
series and basic knowledge about the productivity of the species 
[e.g. @vasconcellos2005; @martell2013]. Recently, @rosenberg2014
investigated the ability for four such models to estimate population status through
a large-scale simulation experiment. A key finding was that these models
frequently disagree on population status and any one model has relatively poor
predictive ability on average (e.g. Fig. \ref{motivate}).

Here, we estimate population status and trajectory of exploited fish populations
using ensemble and superensemble models (collectively referred to 'ensemble
methods'). We explore a variety of approaches applied to both simulated and
real-world fish stocks and compare predictive performance. We find that
ensembles, and in particular superensembles, generally improved predictive
performance of status and trajectory of fish populations over any single
model---especially when considered across multiple dimensions of predictive
ability and across multiple datasets. Furthermore, the output from
superensembles can aid mechanistic understanding of how individual models of
status and trajectory perform.

@@

We first developed and tested ensemble methods with a fully factorial simulated
dataset [@rosenberg2014]. These previously published simulation models included
three life histories: small pelagic, demersal, large pelagic; three levels of
how depleted biomass was at the start of the dataset compared to carrying
capacity: 100%, 70%, and 40% of carrying capacity; and four exploitation
dynamics: a constant exploitation rate, a exploitation rate that is coupled
with biomass to mimic an open-access single-species fishery, a scenario where
exploitation rate increases to a fixed level, and a 'roller-coaster' scenario
where the exploitation rate increases and then decreases. Process noise was
introduced to the models through two levels of multiplicative recruitment
variability: $N(0, 0.2)$ and $N(0, 0.6)$, and that process noise was either
uncorrelated or had a first-order autoregressive correlation of 0.6. The
simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

@rosenberg2014 ran ten iterations for each combination of
factors adding stochastic draws of recruitment and catch-recording variability
each time to generate a total of 5760 stocks. The simulation models were built
in the package `FLR` [@kell2007] for the statistical software \textsf{R}
[@r2015]. The code to generate the simulations is available at
<https://github.com/flr/StockSims> (TODO: not there).

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database
[@ricard2012]. Our analysis of the stock-assessment database was based on
version XX downloaded on XX. After removing stocks for which the models
described below did not converge, this database included `r ram_stocks_n`
stocks.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year,
$B_t$ represents biomass at time $t$, $r$ represents the intrinsic population
growth rate, $B_0$ represents unfished biomass or carrying capacity, and $C$
represents catch. @rosenberg2014 provide a full summary of
these four methods and code to fit all the models is available in an
accompanying package `datalimited` for the statistical software \textsf{R}. In
summary:

@@

* *COM-SIR* (catch-only-model with sample-importance-resampling) is a coupled
  harvest-dynamics model [@vasconcellos2005]. Biomass is assumed to follow a
  Schaefer model and harvest dynamics are assumed to follow a logistic model.
  The model is fit with a sample-importance-sampling algorithm [@rosenberg2014].

* *SSCOM* (state-space catch-only model) is a hierarchical model that, similar
  to COM-SIR, is based on a coupled harvest-dynamics model [@thorson2013].
  SSCOM estimates unobserved dynamics in both fishing effort and the fished
  population based on a catch time series and priors on $r$, the maximum rate
  of increase of fishing effort, and the magnitude of various sources of
  stochasticity. The model is fit in a Bayesian state-space framework to
  integrate across three forms of stochasticity: variation in effort,
  population dynamics, and fishing efficiency [@thorson2013].

* *mPRM* (modified panel regression model) is a modified version of the
  panel-regression model from @costello2012. Unlike the other
  models, mPRM is empirical and not mechanistic---it uses the RAM Legacy Stock
  Assessment database to fit a regression model to a series of characteristics
  of the catch time series and stock with stock-assessed $B/B_\mathrm{MSY}$ as
  the response. The model used in this paper is modified from the original in
  that it condenses the life-history categories into three categories to match
  the simulated dataset, removes the maximum catch predictor since the absolute
  catch in the simulated dataset is arbitrary, and does not implement the bias
  correction needed in @costello2012 for deriving aggregate
  estimates of mean status across multiple stocks.

@@

Superensemble models allow us to incorporate additional covariates 
and potentially leverage interactions between these covariates and individual
model predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. For simplicity, and to allow us to apply models
developed with the simulated dataset to the real-world dataset, we added only one
set of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the statistical properties of the catch series
that is independent of time series length and absolute magnitude of catch. We fit
spectral models to the scaled catch time series (catch divided by maximum
catch) with the `spec.ar` function in \textsf{R} and recorded representative
short- and long-term spectral densities at frequencies of 0.20 and 0.05, which
correspond to 5- and 20-year cycles.

## Superensemble models

The individual models we seek to combine with superensembles provide time
series of $B/B_\mathrm{MSY}$. Therefore, we can use superensembles to estimate
multiple properties of these status time series. Here, we focus on two
properties: the mean and slope of $B/B_\mathrm{MSY}$ in the last 5 years.
Together, these quantities address the recent state and trajectory of status,
which are both of management and conservation interest [e.g. @mace2008]. To
avoid undue influence of the end points of the time series on the calculated
slope, we measured the slope as the Theil-Sen estimator of median slope
[@theil1950].

Here we compare an ensemble average and three superensembles of varying
complexity: a linear model with two-way interactions, a random forest, and
boosted regression tree. The general form of our models was

@@

\noindent 
where $L$ is a generalized loss function, $f$ is some generalized regression
function, $\hat{b}_\mathrm{CMSY}$ is the mean or slope prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $S(0.2)$ and $S(0.05)$ represent the
spectral density of the scaled catch series at frequencies of 0.20 and 0.05, $b$
is the mean or slope value the model is fitted to, and $\theta$ is the set of
parameters for the regression function. For all superensemble models of mean
$B/B_\mathrm{MSY}$---a ratio bounded at zero---we fit the models in log space
and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$
slope, which are not bounded at zero, we fit superensemble models on the natural
untransformed scale.

We fit the linear model ensemble with second-order interactions. We fit two
machine learning ensemble models based on regression trees. Regression trees
sequentially determine what value of a predictor best splits the response data
into two 'branches' based on a specified loss function [@breiman1984]. In random
forests, a series of regression trees are built on a random subset of the data
and random subset of the covariates of the model [@breiman2001]. In generalized
boosted models (GBMs), each subsequent model is fit to the residuals from the
previous model; data points that are fit poorly in a given model are given more
weight in the next model [@elith2008]. Random forests and GBMs can provide
strong predictive performance and fit highly non-linear relationships
[@elith2008; @hastie2009]. We fit random forest models with the `randomForest`
package [@liaw2002] for \textsf{R} with the default argument values. We fit
boosted regression tree models with the `gbm` package [@ridgeway2015] for
\textsf{R}. Based on cross-validation with the **caret** \textsf{R} package, we
fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate
(shrinkage parameter) of $0.01$, and all other arguments at their default
values.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here,
we measure proportional error, defined as
$(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true'
(or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional
error to measure bias, median absolute proportional error to measure accuracy,
and Spearman's rank-order correlation to measure the ability to correctly rank
populations.

@@

Ensemble models, and in particular the machine learning ensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning ensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These ensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning ensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting the trends of status (SSCOM; Fig.
\ref{performance-sim-slope}).

<!--TODO: check labels on Figure S4 – repeat of (d) and missing (f)-->
The ensemble models were able to improve the predictions of status by
exploiting the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high prediction
clusters (Fig. \ref{partial-sim}). Ensembles also exploited the covariance
between individual model predictions. For instance, both the linear model and
GBM ensemble suggest that if mPRM and SSCOM predict high status, the true
status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The
addition of spectral density covariates helped the ensemble models correctly
predict higher status values (Fig. \ref{hexagon}g, h) by exploiting
interactions between the spectral density predictors and the individual model
predictions (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally
degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

@@

Ensemble methods provide a useful approach to situations where conservation and
ecological resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status---a situation common to many
ecological settings beyond fisheries. Compared to individual models of fish
population status, ensemble methods were consistently the best or among the best
across three performance dimensions (accuracy, bias, and rank-order
performance), two response variables (status and trajectory), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a
simple average to machine learning models). Our results suggest choosing an
superensemble model that allows for non-parametric relationships, such as machine
learning methods. These methods provide added insight into individual model
behaviour and generally performed the best, however even a simple average of
predictions across multiple models may be useful.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make errors in
uncorrelated ways [@ali1996; @dietterich2000; @tebaldi2007]. Such
individual models would be expected to perform well in different conditions and
an ensemble model can exploit the best predictive performance of each. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to over-fitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we applied our ensembles to an
entirely new dataset (Fig. \ref{performance}b) and averages are a common
ensemble approach in climate science [@ipcc2013]. Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically biased
impression of predictive performance if the training dataset fundamentally
differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble models
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. By focussing on
predictions, ensembles do not suffer from the muddled inference of coefficient
averaging when coefficients covary [@cade2015] and are a more general purpose
tool: they do not require information theoretics, they can combine different
types of models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of superensembles is that they can be tailored to specific response
variables. For example, we built separate ensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For example, SSCOM contributed little to the GBM ensemble estimate
of status at higher levels of predicted $B/B_\mathrm{MSY}$, but contributed
strongly to estimates of slope (TODO FIG). Formally, fitting ensemble models to
specific quantities of interest provides an additional calibration step
[@rykiel1996]. Individual models are typically calibrated (i.e. parameters are
estimated) based on a single response variable; however, this model might then
provide a biased or inaccurate estimate of other quantities of interest. For
example, a data-limited fisheries model might calibrate parameters by
maximizing likelihood with respect to observed and predicted catches but those
parameters may then provide a biased or inaccurate estimate of the mean and
slope of $B/B_\mathrm{MSY}$. Ensemble methods provide a final calibration step
to a quantity of interest. This ensemble calibration could further include a
loss function tailored to the goals of the model, say placing greater weight on
accuracy at low status levels than higher values.
